Arrows for Parallel Computations

### 2017-11-23 paper/content/benchmarks.tex
wip on tables

\rmtest is a probabilistic primality test that iterates multiple (32--256 here)
``subtests''. Should a subtest fail, the input is definitely not a
prime. If all $n$ subtest pass, the input is composite with the
probability of $1/4^{n}$.

@@

``Gentleman'' is a standard Eden test program, developed
for their \ensuremath{\Varid{torus}} skeleton. It implements a parallel matrix
multiplication \citep{Gentleman1978}. We ported an Eden based version \citep{Eden:SkeletonBookChapter02} to PArrows.

@@

@@

\newcommand{\speedupJacobiDist}[5]{
\speedupplot{Speedup of \jacobitest \enquote{#2} vs simulated \enquote{#5}}{PArrows #2, simulated PArrows #5}{256}{#3}{
% \addplot [mark=*,very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-parrows-11213-#2.csv};
\addplot [mark=*,very thick,blue] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/distributed-jacobi/bench-jacobi.bench.jacobi-parr-#1-#2.csv};
%\addplot [mark=x,very thick,red] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
%smooth]{benchmarks/distributed-jacobi/bench-jacobi.bench.jacobi-parr-#1-#5.csv};
% \addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-eden-#1-#2.csv};
}{#4}{\plotwidthDist}
}

>>>>

\rmtest is a probabilistic primality test that iterates multiple (32--256 here)
\enquote{subtests}. Should a subtest fail, the input is definitely not a
prime. If all $n$ subtest pass, the input is composite with the
probability of $1/4^{n}$.

@@

\enquote{Gentleman} is a standard Eden test program, developed
for their \ensuremath{\Varid{torus}} skeleton. It implements a parallel matrix
multiplication \citep{Gentleman1978}. We ported an Eden based version \citep{Eden:SkeletonBookChapter02} to PArrows.

@@

\begin{table}[]
\centering
\label{my-label}
\begin{subtable}[t]{.5\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{l R{1cm} R{1.3cm} R{1.3cm}}
		% \multicolumn{3}{c}{worst Sudoku Benchmarks} \\ \hline
		vs.             & cores	& params   & factor \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/worstSudoku.csv}{}{\vs & \nCores & \params & \factor \\}
	\end{tabular}
	\endgroup
    \caption{Sudoku}\label{table1}
\end{subtable}
\caption{Worst Benchmark results}
\end{table}

@@

\newcommand{\speedupJacobiDist}[5]{
\speedupplot{Speedup of \jacobitest \enquote{#2} vs simulated \enquote{#5}}{PArrows #2, simulated PArrows #5}{256}{#3}{
% \addplot [mark=*,very thick] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-parrows-11213-#2.csv};
\addplot [mark=*,very thick,blue] table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
smooth]{benchmarks/distributed-jacobi/bench-jacobi.bench.jacobi-parr-#1-#2.csv};
\addplot [mark=x,very thick,red] table [scatter, x="nCores", y="speedup"/, col sep=comma, mark=none,
smooth]{benchmarks/distributed-jacobi/bench-jacobi.bench.jacobi-parr-#1-#5.csv};
% \addplot table [scatter, x="nCores", y="speedup", col sep=comma, mark=none,
% smooth]{benchmarks/distributed-rm/bench-distributed.bench.skelrm-eden-#1-#2.csv};
}{#4}{\plotwidthDist}
}
